Tracing the Meta-Level: PyPy's JIT Compiler

### 2009-03-31 talk/icooolps2009/paper.tex
kill XXX

This process assumes that the path through the loop that was traced is a
"typical" example of possible paths (which is statistically likely). Of course
it is possible that later another path through the loop is taken, therefore the
machine code will contain \emph{guards}, which check that the path is still the same.
If a guard fails during execution of the machine code, the machine code is left
and execution falls back to using interpretation (there are more complex
mechanisms in place to still produce more code for the cases of guard failures,
but they are of no importance for this paper XXX is that true?).

>>>>

This process assumes that the path through the loop that was traced is a
"typical" example of possible paths (which is statistically likely). Of course
it is possible that later another path through the loop is taken, therefore the
machine code will contain \emph{guards}, which check that the path is still the same.
If a guard fails during execution of the machine code, the machine code is left
and execution falls back to using interpretation (there are more complex
mechanisms in place to still produce more code for the cases of guard failures,
but they are of no importance for this paper).
